sem

### 2023-01-31 scripts/workshop/sem.Rmd
update list formatting

 - Try to incorporate nonlinear regression into model for temperature relationships
  - I want to use a GAM with a smooth term for temperature
 - Check to see if there is a problem without having the directed separation test
  - Still not sure why it says there are no independence claims present when it seems like there is?
  - There seems to be a significant relationship between log10(size) ~ cc that isn't being specified but is showing up under the independence claims result

>>>>

* Try to incorporate nonlinear regression into model for temperature relationships
  + I want to use a GAM with a smooth term for temperature
* Check to see if there is a problem without having the directed separation test
  + Still not sure why it says there are no independence claims present when it seems like there is?
  + There seems to be a significant relationship between log10(size) ~ cc that isn't being specified but is showing up under the independence claims result
